---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HicdepR

<!-- badges: start -->
<!-- badges: end -->

The goal of HicdepR is to provide local `.rds` files that contain the HICDEP
codes (version 1.120) locally to users. In addition, the function `hicdep_scrape.R`
can be used to manually scrape one of the HICDEP tables from the web.

## Installation

HicdepR is currently in development version. You can download it from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bsurial/HicdepR")
```

## Access HICDEP tables

If you need information from a HICDEP table, access it from the list 
`hicdep_data`.

```{r access-data}
library(HicdepR)

hicdep_data$tblART
```


## Manually get a table from HICDEP

If you want to manually scrape a HICDEP page (e.g. an older version than 1.120),
just add the URL and the corresponding name to `hicdep_scrape()`.

```{r scrape-data}
library(HicdepR)

## Get an older version of tblART from HICDEP 1.110
tblART <- hicdep_scrape("https://hicdep.org/Wiki/v/9/pt/3/Table/17", "tblART")
```

For most HICDEP tables, there the function provides a list of 2 tables, 
`corefields` and `additional`. These can be retrieved as with any list items.

```{r}
head(tblART$corefields)
```

